---
title: 'W4: Start with R'
author: "Ruta Slivkaite"
date: "9/26/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r cars}
summary(cars)

#loading libraries
library(tidyverse)

##setting working directory
setwd("C:/Users/Ruta/Documents/Rutos SmuTkes/Introduction to cultural data science/CDS-2020-W4-Start-with-R")
getwd()

```

For this assignment, please submit a page of your journal showing:

1) Install the 'tidyverse' package and use the read_csv() function to read the SAFI_clean.csv dataset into your R project as 'interviews' digital object;



2) Take a screenshot of your RStudio (showing both your new 'interviews' object in the Environment, and the .Rproj file in the bottom right Files window) and post it to your repository inside our Github organisation >teams> CDS2020. Place here the link leading to the repository, where you had posted the screenshot of your R project (showing the file structure).



3) Use R to figure out how many elements in the vector below are greater than 2 . (You need to filter out the NAs first)

<pre class="ql-syntax" spellcheck="false">rooms <- c(1, 2, 1, 1, NA, 3, 1, 3, 2, 1, 1, 8, 3, 1, NA, 1) </pre>



4) Provide the result of the function median() run on the rooms vector.



```{r}

  ##step 1

  ##laoding the data

interviews <- read.csv(file = "~/Rutos SmuTkes/Introduction to cultural data science/CDS-2020-W4-Start-with-R/SAFI_clean.csv")


```

  
```{r}


 ##step 2
  
  #link leading to the repository, where I had posted the screenshot of my R project: https://github.com/Rutatu/CDS-2020-W4-Start-with-R.git

  

  ##step 3

rooms <- c(1, 2, 1, 1, NA, 3, 1, 3, 2, 1, 1, 8, 3, 1, NA, 1) 

  #filtering out the NAs
rooms <- rooms[!is.na(rooms)]


  #calculating elements in the vector "rooms" greater than 2 

rooms[rooms>2]

  #the answer is 4 elemenst are greater than 2

  #calculating the median
median(rooms)

  #the answer is 1


```
  
  
  